This page discusses the simulation results for the system.

Plots showing the motion of both the platform and the ball were generated for multiple initial system conditions in M\+A\+T\+L\+AB. This was accomplished by first linearizing the equations of motion and then simulating the linearized system at different initial ball and platform positions. See \href{https://bitbucket.org/chstanto/me405_labs/src/master/Lab_6/}{\texttt{ https\+://bitbucket.\+org/chstanto/me405\+\_\+labs/src/master/\+Lab\+\_\+6/}} for M\+A\+T\+L\+AB code and more information.



The results for Case A above show the response of the system at equilibrium. It acts exactly as we would expect because when the ball starts directly over the center of the platform there should be no movement in the system.



The results for Case B above show the response of the system when the ball has been offset by 5 cm. The exponential response of both the balls motion and platforms motion is expected because as the ball rolls further from center it should cause a greater moment on the platform, causing the angle to increase and thus increasing the velocity of the ball.



The results for Case C above show the response of the system when the platform has been offset by 5 degrees. The offset causes the ball to begin rolling and increase velocity while the platform continues to rotate further in the direction of the offset.



The results for Case D above show the response of the system after experiencing a minor impulse from the motor. The results show that the impulse causes a small linear region in the angular velocity of the platform, but otherwise has minor effects except to get the ball rolling. All plots show the opposite results of Case C and B because the motor torque causes a negative platform angle and thus the ball rolls in the opposite direction.



The plots above show the response of the system in closed loop. Gains were applied based on the lab handout, but the response shows that ultimately the platform is able to balance the ball when it has been offset by 5 cm. With the improvement of the controller the system should be able to balance the ball without so much oscillation, because ultimately at larger initial offsets that motion could be harmful to the system. 